### 2023-01-25 manuscript.tex
Fixing references to use bibliography [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/76f75247d47f0d152d3ef69cfed06a9feb6ff958.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/76f75247d47f0d152d3ef69cfed06a9feb6ff958/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001679725

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4}{stain/2022-fdo-paper@1c02a3c}
on January 24, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/76f75247d47f0d152d3ef69cfed06a9feb6ff958/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/76f75247d47f0d152d3ef69cfed06a9feb6ff958}{stain/2022-fdo-paper@76f7524}
on January 25, 2023.
